\cvsection{Projects}
\vspace{10pt}
\begin{cventries}
  \cventry
    {Major Qualifying Project}
    {MRI Compatible Fiber Optic Force Sensing}
    {Massachusetts, U.S.A}
    {2016 - Present}
    {
      \begin{cvitems}
        \item {Developed an optical force sensing technique using fiber optics to study the force profiles of tissue for needle \\guidance during a MRI biopsy.}
        \item {Designed a fixture and performed finite element analysis (FEA) to assess strain compatibility with the Fabry-Perot \\Interferometry sensors.}
        \item {Designed a structure to hold and align optical components and a custom PCB.}
      \end{cvitems}
    }
  	\cventry
    {Hackathon Grand Prize Winner - MLH HACK@WPI 2017}
    {ToasterIO - Internet of Things}
    {Massachusetts, U.S.A}
    {Jan 13th-15th 2017}
    {
      \begin{cvitems}
        \item {Modified a toaster to work with the Amazon Echo and a Raspberry Pi 3.}
        \item{Built a pulley system using recycled parts and a DC motor to autonomously pull down the knob.}
        \item{Designed a circuit board by reverse engineering the toaster to connect it to the Raspberry Pi.}
      \end{cvitems}
    }
  \cventry
    {Unified Robotics - Manipulation}
    {2-DOF Arm Manipulation}
    {Massachusetts, U.S.A}
    {Fall 2016}
    {
      \begin{cvitems}
        \item {Designed and implemented a control system for  a 2-DOF automated arm to pick up and weigh blocks moving \\on a conveyor belt.}
       \item {Included embedded programming on the AVR ATmega644P which allowed interfacing with MATLAB and peripherals.}
       \item {Used PID control, forward and inverse kinematics, infrared sensing and current sensing to efficiently perform the task.}
      \end{cvitems}
    }    
	\cventry
    {Unified Robotics - Navigation}
    {Path Planning and Mapping}
    {Massachusetts, U.S.A}
    {Spring 2016}
    {
      \begin{cvitems}
        \item {Used a turtlebot equipped with a Kinect and a Kobuki base to map and navigate an unknown area.}
        \item {Implemented a SLAM algorithm using A* and frontier exploration on a ROS and Python platform.}
      \end{cvitems}
     }
	\cventry
    {Unified Robotics - Sensing}
    {Fire Fighting Robot}
    {Massachusetts, U.S.A}
    {Spring 2015}
    {
      \begin{cvitems}
        \item {Designed, built and programmed a robot that navigated through a maze to find and extinguish a flame.}
        \item {Used ultrasonic sensors and heat sensors to successfully navigate and detect fire.}
        \item {A combination of odometry and accelerometer was used to report the location of the robot and the fire.}
      \end{cvitems}
     }
	\cventry
    {Unified Robotics - Actuation}
    {Nuclear Reactor Robot}
    {Massachusetts, U.S.A}
    {Spring 2015}
    {
      \begin{cvitems}
        \item {Designed and built a robot to change fuel rods in a platform that simulated a real-world automated nuclear plant.}
        \item {The robot autonomously navigated through the plant using a line following algorithm.}
        \item {Built a Peaucellier-Lipkin arm to manipulate fuel rods and an Ackermann steering drivetrain for mobility.}
      \end{cvitems}
     }   
    \cventry
    {Spacecraft Mission Analysis and Design}
    {Phobos Exploration Mission Design}
    {Massachusetts, U.S.A}
    {Spring 2017}
    {
      \begin{cvitems}
        \item {Designed a spacecraft and mission to orbit Mars and trail its largest moon, Phobos.}
        \item {Focused on the baseline design for attitude control system by evaluating the moment of inertias of the spacecraft.}
        \item {Designed a trajectory for low thrust propulsion which assisted in developing a baseline for the propulsion and \\power systems.}
      \end{cvitems}
     }
    \cventry
   	{Project Manager \& Developer}
   	{Get There - WPI Navigation Application}
   	{Massachusetts, U.S.A}
   	{Fall 2015}
   	{
      \begin{cvitems}
        \item {Developed a desktop application for navigating the WPI campus in Java.}
        \item {Utilized Java Swing to implement the GUI design.}
        \item{Used Dijkstra's algorithm for path calculations.}
        \item{Heavily involved in the integration of the back-end and front-end subsystems.}
      \end{cvitems}
    }
\end{cventries}

%     \cventry
%     {Interactive Qualifying Project}
%     {\textit{"The Drone Perspective"}}
%     {Massachusetts, U.S.A}
%     {2015-2016}
%     {
%       \begin{cvitems}
%         \item {A Research Project studying the interaction between commercial usage of drones and the society in the past, present and future.}
%         \item {The project resulted in a website: \textit{https://thedroneperspective.wordpress.com/}}
%       \end{cvitems}
%     